Exploiting Array Syntax in Fortran for Accelerator Programming

### 2011-06-23 papers/GPUScA-2011/foropencl.tex
Modified to use ACM style.

\documentclass[10pt, conference, compsocconf]{IEEEtran}

\usepackage{cite}
\usepackage{graphicx}
\usepackage[cmex10]{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{url}
\usepackage{listings}

@@

%%
%% reorder appropriately later
%%
\author{\IEEEauthorblockN{Matthew J. Sottile}
\IEEEauthorblockA{Galois, Inc.\\
%421 SW 6th Ave. Suite 300 \\
%Portland, OR 97204\\
matt@galois.com}
\and
\IEEEauthorblockN{Craig E Rasmussen,\\
                  Wayne N. Weseloh,\\
                  Robert W. Robey}
\IEEEauthorblockA{Los Alamos National Laboratory\\
%CCS-7, MS B287\\
%Los Alamos, NM\\
\{crasmussen, weseloh, brobey\}@lanl.gov}

\and
\IEEEauthorblockN{Daniel Quinlan}
\IEEEauthorblockA{Lawrence Livermore\\ National Laboratory\\
dquinlan@llnl.gov}

\and
\IEEEauthorblockN{Jeffrey Overbey}
\IEEEauthorblockA{University of Illinois\\at Urbana-Champaign\\
overbey2@illinois.edu}

}

@@

@@

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,foropencl}

\end{document}

>>>>

\documentclass{acm_proc_article-sp}

\usepackage{cite}
\usepackage{graphicx}
%\usepackage[cmex10]{amsmath}
%\usepackage{amssymb}
%\usepackage{array}
\usepackage{url}
\usepackage{listings}

@@

\numberofauthors{6}

\author{
% 1st. author
\alignauthor
Matthew J. Sottile\\
       \affaddr{Galois, Inc.}\\
       \affaddr{421 SW 6th Ave. Suite 300}\\
       \affaddr{Portland, OR 97204}\\
       \email{matt@galois.com}
% 2nd. author
\alignauthor
Craig E Rasmussen\\
       \affaddr{Los Alamos National Laboratory}\\
       \affaddr{CCS-7, MS B287}\\
       \affaddr{Los Alamos, NM 87545}\\
       \email{crasmussen@lanl.gov}
% 3rd. author
\alignauthor
Wayne N. Weseloh\\
       \affaddr{Los Alamos National Laboratory}\\
       \affaddr{XTD-1, MS T082}\\
       \affaddr{Los Alamos, NM 87545}\\
       \email{weseloh@lanl.gov}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor
Robert W. Robey\\
       \affaddr{Los Alamos National Laboratory}\\
       \affaddr{XCP-2, MS T086}\\
       \affaddr{Los Alamos, NM 87545}\\
       \email{brobey@lanl.gov}
% 5th. author
\alignauthor
Daniel Quinlan\\
       \affaddr{Lawrence Livermore National Laboratory}\\
       \email{dquinlan@llnl.gov}
% 6th. author
\alignauthor
Jeffrey Overbey\\
       \affaddr{University of Illinois at Urbanna-Champaign}\\
       \email{overbey2@illinois.edu}
}

@@

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

@@

\bibliographystyle{abbrv}
\bibliography{foropencl}

\balancecolumns
\end{document}
